MG7: Configurable and scalable 16S metagenomics data analysis -- new methods optimized for massive cloud computing

### 2015-09-14 docs/paper/out/paper.tex
various fixes, add refs etc -- paper

The second step is to search for similar 16S sequences in our 16S-DB7
database. The taxonomic assignment for each read is based on BLASTN of
each read against the 16S database. Assignment based on direct
similarity of each read one by one compared against a sufficiently wide
database is a very exhaustive method for assignment
\citep{segata2013computational} . Some methods of assignment compare the
sequences only against the available complete bacterial genomes or avoid
computational cost clustering or binning the sequences first, and then
doing the assignments only for the representative sequence of each
cluster. MG7 carries out an exhaustive comparison of all the reads under
analysis and it does not applies any binning strategy. Every read is
specifically compared with all the sequences of the 16S database. We
select the best BLAST hits (10 hits by default) obtained for each read
to do the taxonomic assignment.

@@

\subsection{Future-proof}\label{future-proof}

\subsection{MG7 Future developments}\label{mg7-future-developments}

@@

\subsubsection{Comparison of groups of
samples}\label{comparison-of-groups-of-samples}

\subsubsection{Interactive visualizations using the output files of MG7
(Biographika
project)}\label{interactive-visualizations-using-the-output-files-of-mg7-biographika-project}

>>>>

The second step is to search for similar 16S sequences in our 16S-DB7
database. The taxonomic assignment for each read is based on BLASTN of
each read against the 16S database. Assignment based on direct
similarity of each read one by one compared against a sufficiently wide
database is a very exhaustive method for assignment
\citep[\citet{morgan2012chapter}]{segata2013computational}. Some methods
of assignment compare the sequences only against the available complete
bacterial genomes or avoid computational cost clustering or binning the
sequences first, and then doing the assignments only for the
representative sequence of each cluster. MG7 carries out an exhaustive
comparison of all the reads under analysis and it does not applies any
binning strategy. Every read is specifically compared with all the
sequences of the 16S database. We select the best BLAST hits (10 hits by
default) obtained for each read to do the taxonomic assignment.

@@

\subsection{Future developments}\label{future-developments}

@@

\subsubsection{Comparing groups of
samples}\label{comparing-groups-of-samples}

\subsubsection{Interactive visualizations based on
Biographika}\label{interactive-visualizations-based-on-biographika}
